 

### 2024-04-14 outputs/paper.qmd
paper

---
title: "Evidence and Lessons from Public Health Funding's Impact on HIV/AIDS"
author: Ruoxian Wu
thanks: "Code and data are available at: https://github.com/ScarletWu/Funding_Fuels_the_HIV-AIDS_Fight.git. Replication on Social Science Reproduction platform is available at: https://www.socialsciencereproduction.org/reproductions/1783/"
date: "April 2, 2024"
date-format: long
abstract: "This paper replicates and critically examines the study conducted by Marcus Dillender (2023) on the impact of the Ryan White CARE Act's Title I funding on HIV/AIDS outcomes. My replication focuses on the study's methodology, data integrity, and the robustness of its conclusions, particularly in the context of diagnosis and prevalence data. I assess the original findings through a reanalysis of public data sources and discuss the implications of our results for public health policy and future research directions."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

>>>>

---
title: " "
author: Ruoxian Wu
thanks: "Code and data are available at: https://github.com/ScarletWu/Funding_Fuels_the_HIV-AIDS_Fight.git. Replication on Social Science Reproduction platform is available at: https://www.socialsciencereproduction.org/reproductions/1783/"
date: "April 2, 2024"
date-format: long
abstract: " "
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
